---
title: "Data Wrangling Excercise 1"
author: "Afif"
output: github_document

---

##Introduction and Preparation
Purpose of this exercise is to work with a toy data set showing product purchases from an electronics store.While the data set is small and simple, it still illustrates many of the challenges you have to address in real-world data wrangling.

First step of solving this excercise is to load the necessary libraries, and the dataset.
```{r}
library(dplyr)
library(stringr)
refine <- tbl_df(read.csv("refine.csv"))
```
***


##Clean up brand names
Next is to clean up the 'company' column so all of the misspellings of the brand names are standardized.

Unique brand names currently registered in the data frame are as follows:
```{r}
refine %>%
  select(company) %>%
  distinct()
```

From the data above, we know that there should be only four correct company names : phillips, akzo, van houten, and unilever.
To correct these mispelling names, the following coding is used.  
```{r warning=FALSE}
correct.company <- data_frame(initial=c('ph','fi','ak','va','un'),correct_name= c('phillips','phillips','akzo','van houten','unilever'))

buffer <- refine %>%
            mutate(initial=tolower(substr(company,1,2)))
buffer1<-left_join(correct.company, buffer)
buffer1$company<- buffer1$correct_name
refine <- buffer1 %>% select(-correct_name, -initial)
```

As the result of above data wrangling process we get these following unique company names in the dataset:
```{r}
refine %>%
  distinct(company)
```

Which in this case, we can conclude that company names have been successfully standarized.

***

##Separate Product code and number

Next is to separate the product code and number from Product.code...number attribute into two separates variables.

```{r}
refine <- refine %>% mutate(product_code=sub("-.*","",Product.code...number),product_number=sub(".*-","",Product.code...number))%>% 
          select(-Product.code...number)
refine%>%
  select(company, product_number,product_code)%>%
  sample_n(10)
```

***

##Add Product Categories
In order to make data more readable, product codes will be changed to the following product categories:
```{r}
product.categories <- data_frame(code=c("p","v","x","q"),category=c("Smartphone","TV","Laptop","Tablet"))
product.categories
```

```{r}
buffer4 <- data_frame(category=refine$product_code)
buffer4[]<-product.categories$category[match(refine$product_code, product.categories$code)]
refine$category <- buffer4$category
refine%>%
  select(company,product_code,category)%>%
  sample_n(10)
```

****

##Add Full Address for Geocoding
To view the customer information on a map, the addresses need to be in a form that can be easily geocoded. Create a new column full_address that concatenates the three address fields (address, city, country), separated by commas.


```{r}
refine%>%
  mutate(full_address=paste(address,city,country,sep=","))%>%
  select(company,address,city,country,full_address)%>%
  sample_n(10)
```

***

##Create dummy variables for company and product category
Next is to create binary variables for each of product and company for further analysis


```{r}
refine<- refine%>% 
         mutate(company_phillips=match(company,"phillips"))%>%
         mutate(company_akzo=match(company,"akzo"))%>%
         mutate(company_unilever=match(company,"unilever"))%>%
         mutate(company_vanhouten=match(company,"van houten"))%>%
         mutate(product_smartphone=match(category,"Smartphone"))%>%
         mutate(product_tv=match(category,"TV"))%>%
         mutate(product_laptop=match(category,"Laptop"))%>%
         mutate(product_tablet=match(category,"Tablet"))
 
refine[is.na(refine)]<-0

```

Result for companies are as follows:
```{r}
refine%>%
  select(company,company_phillips,company_akzo,company_unilever,company_vanhouten)%>%
  sample_n(10)
```

Result for products are as follows:
```{r}
refine%>%
  select(category,product_laptop,product_tv,product_smartphone,product_tablet)%>%
  sample_n(10)
```